The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-12 paper/iphas-dr2.tex
Detailed applications

The number density of stars in the colour-colour
and colour-magnitude space
can be compared against population synthesis models
to create three-dimensional maps of the extinction
across several kpc \citep{Sale2009,Sale2012}.
Such an extinction map based on our catalogue
is to be released in a separate paper
that accompanies this data release (Sale et al., in preparation).

>>>>

Here we have presented only a short qualitative description of the information obtainable from IPHAS colour-colour and colour-magnitude plots.
A more rigourous quantitative analysis of the IPHAS catalogue
can be undertaken to estimate both the stellar density distribution in the Milky Way \citep{Sale2010}
and to create detailed three-dimensional maps of the extinction across several kpc \citep{Sale2009,Sale2012}.
An extinction map based on our catalogue is to be released in a separate paper
that accompanies this data release (Sale et al., in preparation).
